### 2017-05-05 conclusions.tex
first ship

\section{Conclusions and Future Work}
\label{conc}
\comment{
When are two failing test cases due to the same fault?  This paper
demonstrates that
``when they are repaired by the same program mutants'' is a useful answer to
this question.  The problem of causality in executions is hard, and
has long been tied to a notion of similarity of
executions \cite{NearNeighbor,GroceError}. } By using program changes
(produced by mutants) as
causes to determine distance, it is possible to improve on efforts
to identify the set of faults in a large set of redundant compiler failures
\cite{PLDI13} and discover the source code locations of faults
\cite{MUSE,multilingual}.  For a set of more than 2,800 tests and more
than 50 faults, over the Mozilla SpiderMonkey 1.6 JavaScript compiler and
GCC 4.3.0, our methods improve fault identification (``fuzzer taming''), in a statistically significant way
(with effect size of about 3\% improvement), over
the \emph{best} (for each subject program) of over 16 metrics considered in previous work.
Preliminary investigation also shows improvement (for a shared
mutation testing budget) over previous mutant-based fault localization
methods, for the same tests and a subset of 24 faults with known
locations.  Our {\bf Repair} method, in particular, was the only
localization approach to provide any perfect localizations of faults
(it produced 3),
and provided three times as many very-high-quality (ranking the fault
in top 5 locations) localizations as the next best method
\cite{multilingual}  --- 6 such localizations, compared to only 2.
For GCC wrong-code faults, only our methods produced any very-high-quality fault localizations.

>>>>

\section{Conclusions and Future Work}
\label{conc}
\comment{
When are two failing test cases due to the same fault?  This paper
demonstrates that
``when they are repaired by the same program mutants'' is a useful answer to
this question.  The problem of causality in executions is hard, and
has long been tied to a notion of similarity of
executions \cite{NearNeighbor,GroceError}. } By using program changes
(produced by mutants) as
causes to determine distance, it is possible to improve on efforts
to identify the set of faults in a large set of redundant compiler failures
\cite{PLDI13} and discover the source code locations of faults
\cite{MUSE,multilingual}.  For a set of more than 2,800 tests and more
than 50 faults, over the Mozilla SpiderMonkey 1.6 JavaScript compiler and
GCC 4.3.0, our methods improve fault identification (``fuzzer taming''), in a statistically significant way
(with effect size of about 3\% improvement), over
the \emph{best} (for each subject program) of over 16 metrics considered in previous work.
Preliminary investigation also shows improvement (for a shared
mutation testing budget) over previous mutant-based fault localization
methods, for the same tests and a subset of 24 faults with known
locations.  Our {\bf Repair} method, in particular, was the only
localization approach to provide any perfect localizations of faults
(it produced 3),
and provided three times as many very-high-quality (ranking the fault
in top 5 locations) localizations as the next best method
\cite{multilingual}  --- 6 such localizations, compared to only 2.
For GCC wrong-code faults, only our methods produced any
very-high-quality fault localizations.  When applied to non-compiler
faults, the metric tended to either not produce a localization,
produce a very small incorrect localization (1-3 statements), or
produce a very high quality localization.  Restricting to the cases
where we consider {\bf Repair} applicable (7 faults) {\bf Repair}
perfectly localized 4 of them, and produced a 1 or 2 statement
incorrect localization for the others.

### 2017-05-05 experiments.tex
first ship

The other way to think about {\bf Repair} for the non-compiler faults especially, is as a very \emph{cautious} localization.  It only uses mutants that repair a failure, and, because it is clear that, in general, failing tests contain far more information about faults than passing tests, it only uses information from failures (other than using passing tests to prune mutants that kill some passing tests, again a principle of discarding potentially confusing information).  This results in {\bf Repair} either providing a ``useful'' localization or almost no localization information at all to mislead a user, for the non-compiler faults, which user studies and surveys suggest is the ideal behavior due to the cost of false positives in localization \cite{AutoHelp,Kochhar}.

@@

\subsubsection{Mutation Analysis Costs}

>>>>

The other way to think about {\bf Repair} for the non-compiler faults especially, is as a very \emph{cautious} localization.  It only uses mutants that repair a failure, and, because it is clear that, in general, failing tests contain far more information about faults than passing tests, it only uses information from failures (other than using passing tests to prune mutants that kill some passing tests, again a principle of discarding potentially confusing information).  This results in {\bf Repair} either providing a ``useful'' localization or almost no localization information at all to mislead a user, for the non-compiler faults, which user studies and surveys suggest is the ideal behavior due to the cost of false positives in localization \cite{AutoHelp,Kochhar}.  This is basically a trade-off.  MUSE, MUSEUM, and Metallaxis-FL provide localization for many more faults, in a more diverse range of settings (with single failing tests, no repairs, etc.), and using more diverse information --- but, in cases where {\bf Repair} provides a localization, it seems to often be higher quality due to its restriction to high-signal source of information (mutants repairing failing tests, only).  In settings, unlike compilers, where there are relatively few repairs, {\bf Repair} also produces very little incorrect information, and so has a low cost to the user in terms of wasted attention.  Note that our heuristic to stop reading after 5 wrong localizations is not even needed for all but one CoreUTILS fault --- {\bf Repair} suggests 1-3 statements at most.

@@

\subsection{Mutation Analysis Costs}

### 2017-05-05 relatedwork.tex
first ship

The use of distance metrics in software engineering includes some of the localization and fault identification efforts discussed above (e.g., \cite{NearNeighbor,GroceError,ChakiLev,Liu06}).  Vangala et al. proposed using distance to cluster test cases to improve diversity and eliminate duplicates \cite{VangalaDist}.  We speculate that using FPF with our causal metric over passing tests as a test prioritization (or selection) method might be a fruitful approach \cite{YooHarman}.  Adaptive random testing uses distances (usually between inputs) to choose tests \cite{Chen,ARTChen,ISSTAART}, and Artzi et al. guided test generation for fault localization using path constraint metrics \cite{ArtziDirected}.  Sumner et al. evaluated approaches to generating execution peers for debugging and understanding \cite{Sumner2011} using tree edit distances (and evaluated other distances).  Xin et al. \cite{Xin2008} examined methods for indexing program executions, useful in all methods involving execution alignments.  To our knowledge, most metrics used are essentially spectrum-based \cite{RepsSpectra,BallConcept} (using counts over structural entities), while our metric is essentially causal, based on counterfactual \cite{LewisCause,LewisCount} programs.

>>>>

The use of distance metrics in software engineering includes some of the localization and fault identification efforts discussed above (e.g., \cite{NearNeighbor,GroceError,ChakiLev,Liu06}).  Vangala et al. proposed using distance to cluster test cases to improve diversity and eliminate duplicates \cite{VangalaDist}.  We speculate that using FPF with our causal metric over passing tests as a test prioritization (or selection) method might be a fruitful approach \cite{YooHarman}.  Adaptive random testing uses distances (usually between inputs) to choose tests \cite{Chen,ARTChen,ISSTAART}, and Artzi et al. guided test generation for fault localization using path constraint metrics \cite{ArtziDirected}.  Sumner et al. evaluated approaches to generating execution peers for debugging and understanding \cite{Sumner2011} using tree edit distances (and evaluated other distances).  Xin et al. \cite{Xin2008} examined methods for indexing program executions, useful in all methods involving execution alignments.  To our knowledge, most metrics used are essentially spectrum-based \cite{RepsSpectra,BallConcept} (using counts over structural entities), while our metric is essentially causal, based on mutants as counterfactual \cite{LewisCause,LewisCount} versions of a program.
